---
title: "RAPInetMHCpan"
author: "Elmer A. Fernández"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{RAPInetMHCpan}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
This is an R Application Program Interface for the well known softwares [netMHCpan](https://services.healthtech.dtu.dk/service.php?NetMHCpan-4.0) and [netMHCIIpan](https://services.healthtech.dtu.dk/service.php?NetMHCIIpan-3.2). The RAPInetMHCpan package allows easy deployment of such softwares into your own machine, facilitates their used trhrough full R code and allow multicore processing.


## Installing netMHCpan and netMHCIIpan

The RAPInetMHCpan library allows you installing both softwares from their tar ball zipped files (up to now only version 4.0 for both softwares).
NOTE: please red and follow the [Readme](https://github.com/elmerfer/RAPInetMHCpan) from the main github page.

From [Technical University of Denmark](https://services.healthtech.dtu.dk/) follow the instructions and fill the form to receive the rights to download [netMHCpan](https://services.healthtech.dtu.dk/service.php?NetMHCpan-4.0) and [netMHCIIpan](https://services.healthtech.dtu.dk/service.php?NetMHCIIpan-3.2). Save them to your favorite directory ("/home/../myfavoritedir/..").

Open an R session or RStudio and type:
```R
installNetMHCPan(file = "/home/.../myfavoritedir/netMHCpan-4.0a.Linux.tar.gz" , data = NULL, dir = "/where i whant/dir")
installNetMHCIIPan(file = "/home/.../myfavoritedir/netMHCIIpan-4.a.Linux.tar.gz" , data = NULL, dir = "/where i whant/dir")
```
It will print on console:

`netMHCpan Installation OK`

or

`netMHCIIpan Installation OK`



## Running 
```{r, fig.show='hold'}
library(seqinr)
library(stringr)
library(BiocParallel)
library(openxlsx)
library(RAPInetMHCpan)

#this sequence segment belongs to NA H5N1 .[(GenBank: AAC32089.1)
myseq <- s2c("MNPNQKIITIGSICMVVGIISLMLQIGNIISVWVSHIIQTWHPNQPEPCNQSINFYTEQAAASVTLAGNSSLCPISGWAIYSKDNSIRIGSKGDVF")

seqfile <- file.path(.libPaths()[1],"filetest.fasta")
write.fasta(myseq, file.out = seqfile,
            name = "NA H5N1 .[(GenBank: AAC32089.1) short sequence]")
if(!file.exists(seqfile)){
  stop("ERROR: pls check path")
}
##Run for a unique allele for MHC I
t <- Sys.time()
ret <- RunNetMHCPan(seqfile = seqfile, allele = "HLA-A01:01")
print(Sys.time()-t)
knitr::kable(ret, "pandoc")
```
These table shows the RAPIMHC result class objects with the.

The following plot shows the first Peptide and its interaction core  surrounded by squares. The intermediate segment refers to a "deletion"  interpreted as a peptide segment bulging out from the MHC binding cleft.
```{r, fig.show='hold'}
PlotPeptideCore(eDB = ret, index = 1)
```

The following function will display all the Peptides logo of different lengths. If several peptides of the same length are found, they will be displayed together.
```{r, fig.show='hold'}
PeptideBindersLogo(eDB = ret)
```


