---
title: "RAPInetMHCpan"
author: "Elmer A. Fernández"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{RAPInetMHCpan}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
This is an R Application Program Interface for the well known softwares [netMHCpan](https://services.healthtech.dtu.dk/service.php?NetMHCpan-4.0) and [netMHCIIpan](https://services.healthtech.dtu.dk/service.php?NetMHCIIpan-3.2). The RAPInetMHCpan package allows easy deployment of such softwares into your own machine, facilitates their used trhrough full R code and allow multicore processing.


## Installing netMHCpan and netMHCIIpan

The RAPInetMHCpan library allows you installing both softwares from their tar ball zipped files (up to now only version 4.0 for both softwares).
NOTE: please red and follow the [Readme](https://github.com/elmerfer/RAPInetMHCpan) from the main github page.

From [Technical University of Denmark](https://services.healthtech.dtu.dk/) follow the instructions and fill the form to receive the rights to download [netMHCpan](https://services.healthtech.dtu.dk/service.php?NetMHCpan-4.0) and [netMHCIIpan](https://services.healthtech.dtu.dk/service.php?NetMHCIIpan-3.2). Save them to your favorite directory ("/home/../myfavoritedir/..").

Open an R session or RStudio and type:
```R
installNetMHCPan(file = "/home/.../myfavoritedir/netMHCpan-4.0a.Linux.tar.gz" , data = NULL, dir = "/where i whant/dir")
installNetMHCIIPan(file = "/home/.../myfavoritedir/netMHCIIpan-4.a.Linux.tar.gz" , data = NULL, dir = "/where i whant/dir")
```
It will print on console:

`netMHCpan Installation OK`

or

`netMHCIIpan Installation OK`



## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
